Updates on the Exoplanet Orbit Database

### 2014-02-17 draft/ms.tex
First paragraph of instroduction and added references.

>>>>

Since the first peer-reviewed list of exoplanets with robust orbits
\citep{Butler2002,Butler2006}, the count of exoplanets has increased
from less than 200 to over 1000 today (exoplanets.org). Before the
launch of NASA's \kepler\ mission \citep{Borucki2010}, most confirmed
exoplanets were discovered via the precise radial velocity (RV)
method. However, since 2009, \kepler\ has contributed over $\sim$ 400
confirmed exoplanets (ZZZ need citation update once the $>300$
\kepler\ release comes out) as well as over 3000 exoplanet candidates
(\kepler\ Objects of Interest, KOIs; e.g.~\citealt{Batalha2013}).
